Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-07 main.tex
Tweak
wip

Formal definition.

>>>>

\begin{itemize}
\item
  Idea of accessibility: set of data memory addresses that can be read or written at a particular execution point.
  (Assume instruction memory is distinct.)
\item
  Stack protection intuition in a nutshell: caller's memory data is not accessible to callee, although callee's memory data is accessible to caller.
  This gives both an integrity property (callee cannot affect caller's memory) and a secrecy property
  (caller's memory cannot affect callee).
  Can generalize to other control situations, such as coroutines, threads, compartments,...
\item
  In NI terms, protected programs are oblivious to variations in memory outside of their accessible set.
  Unlike standard NI, the accessible set changes dynamically, so we cannot just frame the property in terms of
  variant start states. [Is this true? Is it a significant difference? Are there other significant differences?]
\item
  We start with a very simple (and unrealistic) set of assumptions/conventions for stack frames and procedure calls:
  \begin {itemize}
  \item All memory (except for instructions) forms a single contiguous stack, divided into frames, each associated with a procedure activation.
  \item Each frame consists of a saved return address and a single word of local data. These form the entirety of the procedure's memory data, and are the only thing we need to track when considering accessibility.
  \item Registers other than RA, SP are not affected by calls or returns and hence are the (only) way to pass values between caller and callee.
  \item Instructions serving as calls are statically marked as such in the code.
  \item The code for each procedure is bracketed by fixed entry and exit sequences (details to follow), which save/restore the RA and
    adjust the SP.  
  \item During the body of the procedure, the single word of local data is accessed via SP, which does not change (except during a call, of course).  The stored RA in the frame never changes. [I'm confused about these. Are they assumptions, or do they have a different status?  We use tags to check them, but should we?]
  \end {itemize}
\item
  Describe conjecture 2 property in terms of this model: informally and formally.
\item 
  Define abstract state descriptions.
\item
  Define step consistency.
\item
  Discuss relationship between state consistency and conjecture 2 property.  (Former is: presumably stronger; hopefully not
  too strong that it produces lots of undesired test failures; surely easier to test).

\end{itemize}
